PANNEURO_analysis

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
mem questions

```{r source file path}
#source data directory: data_path
source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
```

@@

```{r}

dat.raw$bmi[is.infinite(dat.raw$bmi)] = NA

dat.raw <- dat.raw %>%
  mutate(
  bmi.categories=cut(dat.raw$bmi, breaks=c(-Inf, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55,  Inf), labels=c("too low","10 and less","10 to 15", "15 to 20", "20 to 25", "25 to 30", "30 to 35", "35 to 40", "40 to 45", "45 to 50", "50 to 55")))

```{r bmi_category per Sample prop per total}

bmi_category_per_Covid_prop_total <- dat.raw %>%
  count(bmi.categories, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

options(knitr.kable.NA = '')
kable(bmi_category_per_Covid_prop_total)
bmi_category_per_Covid_prop_total
```
```{r bmi_category per Sample prop per Sample}
bmi_category_per_Sample_prop_Sample <- dat.raw %>%
  group_by(Sample) %>%
  count(bmi.categories, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(bmi_category_per_Sample_prop_Sample)
bmi_category_per_Sample_prop_Sample
```

@@

## CFS

@@

```{r}
dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
```

@@

>>>>

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

@@

## BMI not available

@@

```
##CFS

@@

```{r}
dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
dat.raw$cfs.how_is_your_memory_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
```

@@

##memory

```{r, echo = FALSE}

dat.raw[616] <- data.frame(dat.raw[616] %>%
             map(lfactor, levels = c(0,1), labels = c("same/better", "worse")))

mem.table <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.how_is_your_memory)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, cfs.how_is_your_memory) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(mem.table)
```

```{r, echo = FALSE}

mem.table2 <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.how_is_your_memory_binary)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, cfs.how_is_your_memory_binary) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(mem.table2)
```
